### 2015-03-02 fundamentals/impl.tex
reducing the length of sentence about subprocess tests. Keeps to the point: we use nose to do the comparison for each input file.

Integration tests combine multiple elements of the
\Cyclus interface and test that they work correctly with each other.  By analogy,
simply because the gears (units) are made correctly does not imply that the
clock (integration) will run smoothly, run at all, or give the correct time.
In \Cyclus and \Cycamore, integration tests are performed by running sample
simulations for scenarios that are sufficiently simple to predict the results and verifying
        that results match those predictions. A set of standard input files have thus been constructed.
Python is used to run the same set of \Cyclus simulations as a subprocess for each integration test.
 The results are then inspected and compared via Nose \cite{pellerin_nose_2007}, a Python test framework.
In this way, \Cyclus code units are tested in the full context that they will be
executed. This category of testing is especially useful for ensuring that
major \Cyclus components are functioning as expected.

>>>>

Integration tests combine multiple elements of the
\Cyclus interface and test that they work correctly with each other.  By analogy,
simply because the gears (units) are made correctly does not imply that the
clock (integration) will run smoothly, run at all, or give the correct time.
In \Cyclus and \Cycamore, integration tests are performed by running sample
simulations for scenarios that are sufficiently simple to predict the results
and verifying that results match those predictions. A set of standard input
files are run, then the output is inspected and compared via Nose
\cite{pellerin_nose_2007}, a Python test framework.  In this way, \Cyclus code
units are tested in the full context that they will be
executed. This category of testing is especially useful for ensuring that
major \Cyclus components are functioning as expected.
